---
title: "Stan Model of AQI data"
author: "Michael Andreae"
output: html_document
---

# Insurance status predicts antiemetic use 
we build a random effects model with procedure as random effects

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
library(rstan)
library(rstanarm)

# library(nlme)
```



```{r, global_options, echo=FALSE}
# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
rm(list = ls())
everything<-FALSE
```

```{r cores}
library(parallel)
detectCores()
```

# Load cleaned complete case dataset
 
we load the cleaned dataset with procedure information *ccAQI_cpt_cpt.Rdata* which we generated in the Project *AQI_Import*, updated on 29Oct2015.   


```{r, load_clean_dataset, echo=TRUE}
load("Data/myAQI_cpt.Rdata")
str(ccAQI_cpt)
```

# Logit Models

# Four Predictors

## Fixed Effects Model 

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

fit_log2.0 <- glm(formula2.0, 
             family = binomial(link = "logit"), 
             data = ccAQI_cpt)
```

## Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

m2.0 <- glmer(formulaR2.0, data = ccAQI_cpt, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(fit_log2.0, m2.0, file = "Results/results2.0.Rdata")
```


```{r}
load("Results/results2.0.Rdata")
```

### Details Fixed Effects

```{r}
summary(fit_log2.0)
p_values <- summary.glm((fit_log2.0))$coefficient[,4]
ORfixed2.0 <- exp(coef(fit_log2.0)) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(ORfixed2.0, p_values), digits = 3, caption = "Results log2.0")
```

### Details Random Effects

```{r}
summary(m2.0)
ORrandom2.0 <- exp(m2.0@beta) # exponentiated coefficients
```


### Random v. Fixed Side by Side 

```{r}
compareCoef2.0 <- data.frame(random=m2.0@beta, fixed=coef(fit_log2.0))
kable(compareCoef2.0, caption = ("Coefficients"))

compareOR2.0 <- data.frame(random=ORrandom2.0, fixed= ORfixed2.0)
kable(compareOR2.0, caption = ("Odds ratios"))
```

# Stan Models

## Stan Fixed Effects Model 

### Model

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log2.0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

stanfitfix2.0 <- stan_glm(formula2.0, 
             family = binomial(link = "logit"), 
             data = ccAQI_cpt,
             iter= 1000, cores= 2)

save(stanfitfix2.0, file = "Results/stanfitfix2.0.Rdata")
```

### Results Stan fixed effects

```{r}
load("Results/stanfitfix2.0.Rdata")
summary(stanfitfix2.0)
print(stanfitfix2.0)
stan_plot(stanfitfix2.0)
```

## Stan Random Effects Model

### Mixed effects model with one random effect

fitted with stan_glmer and procedure as random effect does run into memory problems:

    
```{r eval=everything, echo=TRUE}
library(rstanarm)
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)
#options(warn=2)
options(warn=0)
stanfit2.0 <- stan_glmer(formulaR2.0, data = ccAQI_cpt, family = binomial, chains = 4, iter=100, cores =4)

save(stanfit2.0, file = "Results/stanfit2.0.Rdata")
```
 
 Error: cannot allocate vector of size 2.7 Gb 
 
This error was overcome by increasing RAM and changing the program with Jonah.

### reducing the data set/ number of random effects
We try to fit the same model on fewer random effects by reducing to a smaller dataset.

#### 30% reduction
```{r, everything = TRUE}
reduxAQI <- ccAQI_cpt[1:30000,]
length(unique(reduxAQI$cpt))
length(unique(ccAQI_cpt$cpt))
save(reduxAQI, file = "Results/reduxAQI.Rdata")
```

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

stanfitredux2.0 <- stan_glmer(formulaR2.0, data = reduxAQI, family = binomial, iter= 1000, cores =2)

save(stanfitredux2.0, file = "Results/stanfitredux2.0.Rdata")
```

#### 50% reduction
```{r}
redux50AQI <- ccAQI_cpt[1:50000,]
length(unique(redux50AQI$cpt))
length(unique(ccAQI_cpt$cpt))
```

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

stanfitredux50p2.0 <- stan_glmer(formulaR2.0, data = redux50AQI, family = binomial, iter= 1000, cores =2)

save(stanfitredux50p2.0, file = "Results/stanfitredux50p2.0.Rdata")
```

### Mixed effects model fitted with 2 random effects

```{r eval=everything, echo=TRUE}
formulaR3.0 <- ond ~ pay +age_group +sex + (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfitredux50p3.0 <- stan_glmer(formulaR3.0, data = reduxAQI, family = binomial, iter= 1000, cores =2)

save(stanfitredux50p3.0, file = "Results/stanfitredux50p3.0.Rdata")
```

### Mixed effects model fitted with 2 random effects for full data set

```{r eval=everything, echo = TRUE}
require(rstanarm)
rm(stanfit3.0)
formulaR3.0 <- ond ~ pay +age_group +sex + (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit3.0 <- stan_glmer(formulaR3.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 500, cores =4)

save(stanfit3.0, file = "Results/stanfit 3.0.Rdata")
```

### Mixed effects model fitted with 2 random effects for full data set

```{r eval=everything, echo = TRUE}
require(rstanarm)
rm(stanfit4.0)
formulaR4.0 <- ond ~ pay +age_group +sex + (1 | cpt) + (prov | practice)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit4.0 <- stan_glmer(formulaR4.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 100, cores =4)

save(stanfit4.0, file = "Results/stanfit4.0.Rdata")
```

FormulaR4.0 seems to get stuck in warm up

### Mixed effects model fitted with hierarchical random effects for full data set

```{r eval=everything, echo = TRUE}
require(rstanarm)
rm(stanfit5.0)
formulaR5.0 <- ond ~ pay +age_group +sex + (cpt | prov) 

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit5.0 <- stan_glmer(formulaR5.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 10, cores =4)

save(stanfit5.0, file = "Results/stanfit5.0.Rdata")
```

FormulaR5.0 runs into memory problems:
stanfit5.0 <- stan_glmer(formulaR5.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 10, cores =4)
Warning messages:
1: In as.vector(mm[, ii]) :
  Reached total allocation of 12287Mb: see help(memory.size)
2: In as.vector(mm[, ii]) :
  Reached total allocation of 12287Mb: see help(memory.size)
3: In as.vector(mm[, ii]) :
  Reached total allocation of 12287Mb: see help(memory.size)
4: In as.vector(mm[, ii]) :
  Reached total allocation of 12287Mb: see help(memory.size)
 Show Traceback
 
 Rerun with Debug
 Error in t(do.call(sparseMatrix, do.call(rBind, lapply(seq_along(blist),  : 
  error in evaluating the argument 'x' in selecting a method for function 't': Error: cannot allocate vector of size 13.2 Gb 
  
### More fixed effects with two random effects model

```{r eval=everything, echo = TRUE}
require(rstanarm)
load("Data/ccAQI_cpt.Rdata")
rm(stanfit6.0)
formulaR6.0 <- ond ~ pay + age_group + sex + ASA + anes_type + 
  (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit6.0 <- stan_glmer(formulaR6.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 500, cores =4)

save(stanfit6.0, file = "Results/stanfit6.0.Rdata")
```

### even more fixed effects with two random effects model

```{r eval=everything, echo = TRUE}
require(rstanarm)
load("Data/ccAQI_cpt.Rdata")
rm(stanfit7.0)
formulaR7.0 <- ond ~ pay + age_group + sex + ASA + anes_type + practice +
  (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit7.0 <- stan_glmer(formulaR7.0, data = ccAQI_cpt, family = binomial, chains = 4, iter= 500, cores =4)

save(stanfit7.0, file = "Results/stanfit7.0.Rdata")
```

### emax model with log Link and two random effects model

```{r eval=everything, echo = TRUE}
require(rstanarm)
require(shinystan)
load("Data/myAQI_cpt.Rdata")
formulaR7.any <- any ~ pay + age_group + sex + ASA + anes_type + practice +
  (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit7.any <- stan_glmer(formulaR7.any, data = ccAQI_cpt, family = binomial, chains = 4, iter= 500, cores =4)

save(stanfit7.any, file = "Results/stanfit7.any.Rdata")

# Generate shinystan files to hasten launch

## without ppcheck data
shiny7.any <- as.shinystan(stanfit7.any, ppd = FALSE)
save(shiny7.any, file = "Results/shiny7.any.Rdata")

## With ppcheck data, which will take longer
ppshiny7.any <- as.shinystan(stanfit7.any)
#ppshiny7.any <- launch_shinystan(stanfit7.any)
save(ppshiny7.any, file = "Results/ppshiny7.any.Rdata")
```


```{r}
# Call shinystan to visualize results and check convergence
load("Results/shiny7.any.Rdata")
launch_shinystan(shiny7.any)
```

# Posterior predictive checking of Model
```{r}
require(rstanarm)
rm(list=ls())
rm(stanfit7.any)
load("Results/ppshiny7.any.Rdata")
load("Results/stanfit7.any.Rdata")

class(stanfit7.any)
ppcheck(stanfit7.any, check = "resid", nreps = 2)
ppcheck(stanfit7.any, check = "test", test = mean)
ppcheck(stanfit7.any, check = "test", test = sd)
ppcheck(stanfit7.any, check = "dist", overlay = FALSE)

```

```{r}
library(mailR)
sender <- "mhandreae@gmail.com"
recipients <- c("mhandreae@gmail.com")
send.mail(from = sender,
          to = recipients,
          subject="FromR to you",
          body = "done with project",
          smtp = list(host.name = "smtp.gmail.com", port = 465, 
                      user.name="mhandreae@gmail.com", passwd="0okm0okm",
                      ssl=TRUE),
          authenticate = TRUE,
          send = TRUE)
```

### Income median as predictor with and without two random effects model

```{r eval=everything, echo = TRUE}
rm(list=ls())
require(rstanarm)
require(shinystan)
load("Data/myAQI_cpt.Rdata")
formulaR8.any <- any ~ income + age_group + sex + ASA + anes_type + practice +
  (1 | cpt) + (1 | prov)

# +(prov|hospital) +(surgery|prov|hospital)
# use update to only change component...
# use fit$model <- NULL to remove the data  or fit$data or model=false??

stanfit8.any <- stan_glmer(formulaR8.any, data = ccAQI_cpt, family = binomial(link=logit), chains = 4, iter= 500, cores =4)

save(stanfit8.any, file = "Results/stanfit8.any.Rdata")

# Generate shinystan files to hasten launch

## without ppcheck data
shiny8.any <- as.shinystan(stanfit8.any, ppd = FALSE)
save(shiny8.any, file = "Results/shiny8.any.Rdata")
#```

### Income median quantile as predictor with two random effects model

#```{r eval=everything, echo = TRUE}
rm(list=ls())
require(rstanarm)
require(shinystan)
load("Data/myAQI_cpt.Rdata")
formulaR9.any <- any ~ incomeQ  + age_group + sex + ASA + 
  anes_type + practice + (1 | cpt) + (1 | prov)

stanfit9.any <- stan_glmer(formulaR9.any, data = ccAQI_cpt, family = binomial(link=logit), chains = 4, iter= 500, cores =4)

save(stanfit9.any, file = "Results/stanfit9.any.Rdata")

# Generate shinystan files to hasten launch

## without ppcheck data
shiny9.any <- as.shinystan(stanfit9.any, ppd = FALSE)
save(shiny9.any, file = "Results/shiny9.any.Rdata")

# combine incomeQ and pay

rm(list=ls())
require(rstanarm)
require(shinystan)
load("Data/myAQI_cpt.Rdata")
formulaR10.any <- any ~ incomeQ  +pay + age_group + sex + ASA + 
  anes_type + practice + (1 | cpt) + (1 | prov)

stanfit10.any <- stan_glmer(formulaR10.any, data = ccAQI_cpt, family = binomial(link=logit), chains = 4, iter= 500, cores =4)

save(stanfit10.any, file = "Results/stanfit10.any.Rdata")

# Generate shinystan files to hasten launch

## without ppcheck data
shiny10.any <- as.shinystan(stanfit10.any, ppd = FALSE)
save(shiny10.any, file = "Results/shiny10.any.Rdata")


library(mailR)
sender <- "mhandreae@gmail.com"
recipients <- c("mhandreae@gmail.com")
send.mail(from = sender,
          to = recipients,
          subject="FromR to you",
          body = "done with project",
          smtp = list(host.name = "smtp.gmail.com", port = 465, 
                      user.name="mhandreae@gmail.com", passwd="0okm0okm",
                      ssl=TRUE),
          authenticate = TRUE,
          send = TRUE)

```

# Model with random effects or providers nested in Practice

```{r}

rm(list=ls())
require(rstanarm)
require(shinystan)
load("Data/myAQI_cpt.Rdata")
formulaRn1.any <- any ~ incomeQ + age_group + sex + ASA + 
  anes_type + practice + (1 | cpt) + (prov | practice)

stanfitRn1.any <- stan_glmer(formulaRn1.any, data = ccAQI_cpt, family = binomial(link=logit), chains = 4, iter= 200, cores =4)

save(stanfitRn1.any, file = "Results/stanfitRn1.any.Rdata")

# extract possible inits and then set them
fit0 <- stan_glm(mpg ~ wt + cyl, data = mtcars, iter = 1)
inits <- rstan::get_inits(fit0$stanfit)
inits[[1]]$alpha <- 0.5
fit <- stan_glm(mpg ~ wt + cyl, data = mtcars, init = inits)
# Generate shinystan files to hasten launch

## without ppcheck data
shinyRn1.any <- as.shinystan(stanfitRn1.any, ppd = FALSE)
save(shinyRn1.any, file = "Results/shinyRn1.any.Rdata")
```