---
title: "Stan Model of AQI data"
author: "Michael Andreae"
output: html_document
---

# Insurance status predicts antiemetic use 
we build a random effects model with procedure as random effects

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
library(rstan)
library(rstanarm)
# library(nlme)
```



```{r, global_options, echo=FALSE}
# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
rm(list = ls())
everything<-FALSE
```

```{r cores}
library(parallel)
detectCores()
```

# Load cleaned complete case dataset
 
we load the cleaned dataset with procedure information *myAQI.Rdata* which we generated in the Project *AQI_Import*.   


```{r, load_clean_dataset, echo=TRUE}
load("Data/myAQI.Rdata")
str(myAQI)
```

# Logit Models

# Four Predictors

## Fixed Effects Model 

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

fit_log2.0 <- glm(formula2.0, 
             family = binomial(link = "logit"), 
             data = myAQI)
```

## Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

m2.0 <- glmer(formulaR2.0, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(fit_log2.0, m2.0, file = "Results/results2.0.Rdata")
```


```{r}
rm(list = ls())
load("Results/results2.0.Rdata")
```

### Details Fixed Effects

```{r}
summary(fit_log2.0)
p_values <- summary.glm((fit_log2.0))$coefficient[,4]
ORfixed2.0 <- exp(coef(fit_log2.0)) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(ORfixed2.0, p_values), digits = 3, caption = "Results log2.0")
```

### Details Random Effects

```{r}
summary(m2.0)
ORrandom2.0 <- exp(m2.0@beta) # exponentiated coefficients
```


### Random v. Fixed Side by Side 

```{r}
compareCoef2.0 <- data.frame(random=m2.0@beta, fixed=coef(fit_log2.0))
kable(compareCoef2.0, caption = ("Coefficients"))

compareOR2.0 <- data.frame(random=ORrandom2.0, fixed= ORfixed2.0)
kable(compareOR2.0, caption = ("Odds ratios"))
```

# Stan Models

## Stan Fixed Effects Model 

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

stanfitfix2.0 <- stan_glm(formula2.0, 
             family = binomial(link = "logit"), iter= 100, cores= 2)
save(stanfitfix2.0, file = "Results/stanfitfix2.0.Rdata")

```

## Stan Random Effects Model

fitted with stan_glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

stanfit2.0 <- stan_glmer(formulaR2.0, data = myAQI, family = binomial, iter= 100, cores =2)

save(stanfit2.0, file = "Results/stanfit2.0.Rdata")
```
=======
fit1 <-stan_glm(mpg ~ wt, data = mtcars)

ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
fit <- stan_glm(weight ~ group)
coef(fit)

counts <- c(18,17,15,20,10,20,25,13,12)
outcome <- gl(3,1,9)
treatment <- gl(3,3)
stan_glm(counts ~ outcome + treatment, family = poisson())
}
>>>>>>> origin/master
