---
title: "Stan Model of AQI data"
author: "Michael Andreae"
output: html_document
---

# Insurance status predicts antiemetic use 
we build a random effects model with procedure as random effects

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
library(rstan)
library(rstanarm)
# library(nlme)
```



```{r, global_options, echo=FALSE}
# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
rm(list = ls())
everything<-FALSE
```

```{r cores}
library(parallel)
detectCores()
```

# Load cleaned complete case dataset
 
we load the cleaned dataset with procedure information *myAQI.Rdata* which we generated in the Project *AQI_Import*.   


```{r, load_clean_dataset, echo=TRUE}
load("Data/myAQI.Rdata")
str(myAQI)
```

# Logit Models

# Four Predictors

## Fixed Effects Model 

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

fit_log2.0 <- glm(formula2.0, 
             family = binomial(link = "logit"), 
             data = myAQI)
```

## Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

m2.0 <- glmer(formulaR2.0, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(fit_log2.0, m2.0, file = "Results/results2.0.Rdata")
```


```{r}
load("Results/results2.0.Rdata")
```

### Details Fixed Effects

```{r}
summary(fit_log2.0)
p_values <- summary.glm((fit_log2.0))$coefficient[,4]
ORfixed2.0 <- exp(coef(fit_log2.0)) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(ORfixed2.0, p_values), digits = 3, caption = "Results log2.0")
```

### Details Random Effects

```{r}
summary(m2.0)
ORrandom2.0 <- exp(m2.0@beta) # exponentiated coefficients
```


### Random v. Fixed Side by Side 

```{r}
compareCoef2.0 <- data.frame(random=m2.0@beta, fixed=coef(fit_log2.0))
kable(compareCoef2.0, caption = ("Coefficients"))

compareOR2.0 <- data.frame(random=ORrandom2.0, fixed= ORfixed2.0)
kable(compareOR2.0, caption = ("Odds ratios"))
```

# Stan Models

## Stan Fixed Effects Model 

### Model

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log2.0, echo=TRUE, eval=everything}

formula2.0 <- ond ~ pay +age_group +sex

stanfitfix2.0 <- stan_glm(formula2.0, 
             family = binomial(link = "logit"), 
             data = myAQI,
             iter= 1000, cores= 2)

save(stanfitfix2.0, file = "Results/stanfitfix2.0.Rdata")
```

### Results Stan fixed effects

```{r}
load("Results/stanfitfix2.0.Rdata")
summary(stanfitfix2.0)
print(stanfitfix2.0)
stan_plot(stanfitfix2.0)
```

## Stan Random Effects Model

fitted with stan_glmer and procedure as random effect does run into memory problems:

    
```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

stanfit2.0 <- stan_glmer(formulaR2.0, data = myAQI, family = binomial, iter= 10, cores =2)

save(stanfit2.0, file = "Results/stanfit2.0.Rdata")
```
 
 Error: cannot allocate vector of size 2.7 Gb 
5 structure(.Internal(La_qr(x)), useLAPACK = TRUE, class = "qr") 
4 qr.default(x, tol = .Machine$double.eps, LAPACK = TRUE) 
3 qr(x, tol = .Machine$double.eps, LAPACK = TRUE) at stanreg.R#11
2 stanreg(fit) at stan_glmer.R#95
1 stan_glmer(formulaR2.0, data = myAQI, family = binomial, iter = 10, 
    cores = 2) 
    
 traceback()
5: structure(.Internal(La_qr(x)), useLAPACK = TRUE, class = "qr")
4: qr.default(x, tol = .Machine$double.eps, LAPACK = TRUE)
3: qr(x, tol = .Machine$double.eps, LAPACK = TRUE) at stanreg.R#11
2: stanreg(fit) at stan_glmer.R#95
1: stan_glmer(formulaR2.0, data = myAQI, family = binomial, iter = 10, 
       cores = 2)

### reducing the data set/ number of random effects
We try to fit the same model on fewer random effects by reducing to a smaller dataset.

```{r}
reduxAQI <- myAQI[1:30000,]
length(unique(reduxAQI$cpt))
length(unique(myAQI$cpt))
```

```{r eval=everything, echo=TRUE}
formulaR2.0 <- ond ~ pay +age_group +sex + (1 | cpt)

stanfitredux2.0 <- stan_glmer(formulaR2.0, data = reduxAQI, family = binomial, iter= 1000, cores =2)

save(stanfitredux2.0, file = "Results/stanfitredux2.0.Rdata")
```
